### 2015-01-21 paper.tex
major restructuring for applyRule

Unit propagation magic!

>>>>

SAT solving is based on a technique called unit propagation:
a set of complex Boolean clauses is simplified, starting from single literals and working up to
For instance, the following constraints describe rules for driving a car.

We have a set of variables that can be either true or false:

\begin{verbatim}
can_drive
has_driving_licence
is_over_18
is_drunk
\end{verbatim}

Next, we represent a possible situation in the world. In order to be allowed to drive, a person must have a driving licence and they must not be drunk. This is represented by the clause $can\_drive ∧\wedge has\_driving\_licence ∧\wedge \neg is\_drunk$. Furthermore, from the world knowledge, we know that in order to have a driving licence, one must be over 18. This is represented by the second clause.

\begin{itemize}
%\item $can\_drive \wedge has\_driving\_licence \wedge \neg is\_drunk$,
%\item $has\_driving\_licence \wedge is\_over\_18$, 
\item $\neg is\_over\_18 \vee is\_drunk$
\item $is\_over\_18$
\end{itemize}

Here we have a possible situation in a world: someone is behaving in a way that makes you think of a hypothesis ``either they are underage or drunk''. This is represented by the clause $\neg is\_over\_18 \vee is\_drunk$. Just by this clause we can't solve the reason for the behaviour: it can be one of them or both. Then we get evidence that they are over 18, represented by the clause $is\_over\_18$. Thus we know that the part $\neg is\_over\_18$ of the is not true, so we can eliminate that from the clause. The solution is below: these variables must be true for the situation to be consistent.

\begin{itemize}
\item $is\_drunk$ = True
\item $is\_over\_18$ = True
\end{itemize}
